Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-08 hscc2017/paper.tex
conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions} \label{sec:conclusions}

We have presented a CEGIS-based approach implemented in a tool called \tool,
which uses inductive synthesis in conjunction with an algorithm for
verifying robust closed-loop stability that addresses plant variations as
interval sets as well as FWL uncertainties in digital controllers.  The
present approach is novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound.  In particular, \tool marks the first use of the CEGIS
paradigm, which handles plants with uncertain models and FWL effects over
the digital controller.  Note that implementing this architecture
efficiently requires adjusting the traditional CEGIS refinement loop to the
use of a two-stage verification engine: here the first stage performs fast,
but potentially unsound fixed-point operations, whereas the second stage
restores soundness by validating the operations performed by the first stage
using interval arithmetic.  Our experimental results show that \tool is able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  Future work will be the extension of
this CEGIS-based approach to further classes of systems, including those
with state space.  We will also consider performance requirements while
synthesizing the digital controller.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec:conclusions}

We have presented a CEGIS-based approach implemented in a tool called \tool,
which uses inductive synthesis in conjunction with an algorithm for
verifying robust closed-loop stability that addresses plant variations as
interval sets as well as FWL uncertainties in digital controllers.  The
novelty in our approach is that it is fully automated and algorithmically
and numerically sound.  In particular, \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  Implementing this architecture efficiently requires
adjusting the traditional CEGIS refinement loop to the use of a two-stage
verification engine: here, the first stage performs fast, but potentially
unsound fixed-point operations, whereas the second stage restores soundness
by validating the operations performed by the first stage using interval
arithmetic.  Our experimental results show that \tool is able to synthesize
stable controllers in most benchmarks within a reasonable amount of time
fully automatically.  Future work will be the extension of this CEGIS-based
approach to further classes of systems, including those with state space. 
We will also consider performance requirements while synthesizing the
digital controller.
